### 2024-02-19 docs/manuscript/manuscript.qmd
modificaciones mínimas

We hypothesize that physical fitness will be inversely related to body fat percentage and positively associated with cardiac autonomic response during exercise in older individuals, based on existing literature and theoretical frameworks. In our opinion, it will be essential for this population to have an optimal cardiac autonomic response, characterized by balanced sympathetic and parasympathetic modulation.

@@

However, our results did not evidence a moderating effect of GDS and BAI scores, challenging initial hypothesis. This finding suggests a nuanced interplay between psychological variables and physical/physiological measures in older people, underscoring the need for further research to elucidate underlying mechanisms and variables beyond depression and anxiety. While the lack of moderating effects does not diminish the significance of psychological factors in aging, it highlights the complexity of their influence.

>>>>

We hypothesize that physical fitness will be inversely related to body fat percentage and associated with cardiac autonomic response during exercise in older individuals. In our opinion, it will be essential for this population to have an optimal cardiac autonomic response, characterized by a shift towards sympathetic activity predominance.

@@

However, our results did not evidence a moderating effect of GDS-30 and BAI scores, challenging initial hypothesis. This finding suggests a nuanced interplay between psychological variables and physical/physiological measures in older people, underscoring the need for further research to elucidate underlying mechanisms and variables beyond depression and anxiety. While the lack of moderating effects does not diminish the significance of psychological factors in aging, it highlights the complexity of their influence.
